Supplementary Appendix

### 2023-07-03 manuscript/supplement.qmd
started adding an end-to-end example

@@

Sometimes it is necessary to implement changes to a document or code without wanting to interfere with a current \"`production`\" version of a document or code. However, a researcher may still want to be able to \"`merge`\" back potential changes, e.g. to integrate new analyses into a script or to develop a new set of features or functions to an application. To do this in a safe, transparent and efficient manner, `Git` provides the option to **branch** our repository. The default branch of any repository is the `main` branch.

>>>>

## Example for an end-to-end workflow using Git

This section aims to summarize a minimally commented end-to-end workflow of incorporating and tracking changes for a an analysis step of a RWE study. To that end, we use the same example as in the main manuscript.

Step 1: In case we work with multiple branches (see @sec-branching below), we can first check if we are on the correct branch where we want to implement our changes.

```{bash, eval = FALSE}
# check the current branch
git branch
```

Step 2: Before initiating any new changes, it can be a good idea to check if a collaborator, who may work on the same branch, made any changes.

```{bash, eval = FALSE}
# git pull changes
git pull
```

Step 3: We make changes to the analysis script \`scripts/03_propensity_score_analysis.R\` by adding a title to a plot illustrating the propensity score overlap.

```{r, eval = FALSE}
# load data
library(smdi)
library(gtsummary)
library(tidyverse)
library(here)
library(smdi)

# we use  data from the smdi R package
data <- smdi::smdi_data_complete

# step 1: compute propensity of exposure assignment

# 1.1 select variables to include in propensity 
ps_covars <- data %>% 
  dplyr::select(-exposure) %>% 
  names()

# 1.2: define formula for the GLM
exposure_form <- as.formula(paste("exposure ~ ", paste(ps_covars, collapse = " + ")))

# 1.3: compute odds
exposure_fit <- stats::glm(
  exposure_form,
  data = data,
  family = "binomial"
  )

# 1.4: show odds
odds_table <- exposure_fit %>% 
  gtsummary::tbl_regression(exponentiate = T)

# step 2: compute propensity scores and visualize overlap before matching
exposure_plot <- data %>% 
  dplyr::mutate(ps = fitted(exposure_fit))

# step 3: plot density/overlap before matching
ps_plot <- exposure_plot %>% 
  ggplot2::ggplot(ggplot2::aes(x = ps, fill = factor(exposure))) +
  ggplot2::geom_density(alpha = .5) +
  ggplot2::theme_bw() +
  ggplot2::labs(
    title = "Propensity score overlap",
    x = "Pr(exposure)",
    y = "Density",
    fill = "Exposed"
    )

png(filename = here("figures", "Figure_1_propensity_score_overlap.png"), width = 15, height = 10, units = "in", res=600)
ps_plot + ggplot2::theme(plot.title=element_text(size=70))
dev.off()
```

@@

Sometimes it is necessary to implement changes to a document or code without wanting to interfere with a current "`production`" version of a document or code. However, a researcher may still want to be able to "`merge`" back potential changes, e.g. to integrate new analyses into a script or to develop a new set of features or functions to an application. To do this in a safe, transparent and efficient manner, `Git` provides the option to **branch** our repository. The default branch of any repository is the `main` branch.
